Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes

### 2018-11-15 Ben_Manuscripts/structure_paper/supporting_information.tex
Response to reviewers

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} 
\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{listings}
\usepackage{xr}
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}

@@

\externaldocument[M-]{Final_Draft}
\title{Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
\author{Benjamin J. Coscia \and Jospeh Yelk \and Matthew A. Glaser \and Douglas L. Gin \and Xunda Feng \and Michael R. Shirts}
\date{}

@@

  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/}}  % put all the figures here
  \maketitle

@@

  Based on evidence from section~\ref{M-section:rpi} of the main text, we
  believe it is most likely that the head groups stack somewhere between
  the sandwiched and parallel displaced modes which we studied (Figure~\ref{fig:between_pd}).

@@

  Monomer tails prefer to lie flat rather than tilt with respect to the
  membrane plane. We created a monomer whose tails tilt ca. 30$\degree$ with
  respect to the $xy$ membrane plane.  We added position restraints to the ends
  of the monomer tails with the same force constant as the head groups (see
  section~\ref{section:equilibration}).  As we slowly reduce the force constants,
  the tails begin to tend towards a negligible tilt angle
  (Figure~\ref{fig:tail_tilt}).

@@

  In section~\ref{M-section:slow_dynamics} of the main text, we calculated the
  autocorrelation function of the outer tail either dihedrals pictured
  in Figure~\ref{fig:dihedrals}.

>>>>

\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{amsmath} 
\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{listings}
\usepackage{xr}
\usepackage{array}
\usepackage{authblk}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thesection}{S\arabic{section}}
\renewcommand{\thepage}{S\arabic{page}}  
\renewcommand{\thetable}{S\arabic{table}}

@@

\externaldocument[M-]{Final_Draft}

\title{Supporting Information : Understanding the Nanoscale Structure of Inverted Hexagonal Phase Lyotropic Liquid Crystal Polymer Membranes}
\author[1]{Benjamin J. Coscia}
\author[2]{Joseph Yelk}
\author[2]{Matthew A. Glaser}
\author[1,3]{Douglas L. Gin}
\author[4]{Xunda Feng}
\author[1]{Michael R. Shirts*}
\date{E-mail: michael.shirts@colorado.edu}

\affil[1]{Department of Chemical and Biological Engineering, University of Colorado Boulder, Boulder, CO 80309, USA}
\affil[2]{Department of Physics, University of Colorado Boulder, Boulder CO, 80309, USA}
\affil[3]{Department of Chemistry and Biochemistry, University of Colorado Boulder, Boulder CO 80309, USA}
\affil[4]{Department of Chemical and Environmental Engineering, Yale University, New Haven, Connecticut 06511, USA}

@@

  \bibliographystyle{ieeetr}
  \graphicspath{{./figures/supporting_figures/}}  % put all the figures here
  \maketitle

@@

  Based on evidence from Section~\ref{M-section:rpi} of the main text, we
  believe it is most likely that the head groups stack somewhere between
  the sandwiched and parallel displaced modes which we studied (Figure~\ref{fig:between_pd}).

@@

  Monomer tails prefer to lie flat rather than tilt with respect to the
  membrane plane. We created a monomer whose tails tilt ca. 30$\degree$ with
  respect to the $xy$ membrane plane.  We added position restraints to the ends
  of the monomer tails with the same force constant as the head groups (see
  Section~\ref{section:equilibration}).  As we slowly reduce the force constants,
  the tails begin to tend towards a negligible tilt angle
  (Figure~\ref{fig:tail_tilt}).

@@

  In Section~\ref{M-section:slow_dynamics} of the main text, we calculated the
  autocorrelation function of the outer tail either dihedrals pictured
  in Figure~\ref{fig:dihedrals}.
